RJObject Manual

### 2015-11-16 Documents/manual.tex
A bit of work on the manual

\section{Introduction}
RJObject is a C++ library for implementing certain kinds of hierarchical
models in DNest3.

>>>>

\section{Introduction}
RJObject is a C++ library for implementing certain kinds of trans-dimensional
hierarchical models (basically `mixture models')in DNest3. I developed this
library after realising that many models I was implementing all had this
common structure.
Throughout this manual, I will assume you're proficient at
DNest3. If not, please read the manual for that project first.

\section{Dependencies}
As well as all the DNest3 dependencies, it's best if you add some of DNest3's
directories to your various PATH variables. Specifically, things will work best
if you put the location of the DNest3 libraries (the location of
the {\tt libdnest3.so} file) to your {\tt LIBRARY\_PATH} and
{\tt LD\_LIBRARY\_PATH}. Also add the directory containing the DNest3 header
files ({\tt *.h}) to your {\tt CPLUS\_INCLUDE\_PATH}. Finally, add the
directory containing DNest3's {\tt postprocess.py} and {\tt dnest\_plots.py} to
your {\tt PYTHON\_PATH}.
